The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-09-13 ms.Rmd
spThin module code updated so that it passes tha package checks. There was an issue with indexing in the last lines and I think NAs might have been causing an issue too.

Such a model can be quickly and easily re-constructed as a `zoon` workflow using modules available in the ZOON module repository.
@Feng2015 used a combination of occurrence data from GBIF, and additional occurrence data manually collected from the published literature.
Unfortunately the latter data have not been made publically available, so here we use only data from GBIF.
If the the additional data had been made available it would be straightforward to incorporate them, for example using the `LocalOccurrenceData` module.

@@

  # get dataframe & index to presence data
  df <- .data$df
  pres_idx <- which(df$type == 'presence')

@@

  # get index to rows in sub_df, update the full dataset and return
  pres_keep_idx <- rownames(th[[1]])
  .data$df <- rbind(df[pres_idx[pres_keep_idx], ],
                    df[-pres_idx, ])
  return (.data)
}
```

@@

```{r buildmodule, eval = TRUE, results = 'hide'} 
BuildModule(object = spThin,
            type = 'process',
            title = 'Spatial thinning of Presence-only Data',
            description = paste('Apply the stochastic spatial thinning',
                                'algorithm implemented in the spThin',
                                'package to presence data in a',
                                'presence-background dataset'),
            details = paste('Full details of the algorithm are available in',
                            'the open-access article by Aiello-Lammens',
                            'et al. (2015): dx.doi.org/10.1111/ecog.01132'),
            author = 'ZOON Developers',
            email = 'zoonproject@gmail.com',
            paras = list(thin = paste('Thinning parameter - the required',
                         'minimum distance (in kilometres) between points',
                         'after applying the thinning procedure')),
            dataType = 'presence-only',
            check = TRUE)
```

This module can now be shared so that others can use it in their ZOON workflows. The bexst way of sharing it is via the `zoon` modules repository. Modules can uploaded there, via the module submission system at [URL TBD].

>>>>

Such a model can be quickly and easily re-constructed as a `zoon` workflow using modules available in the ZOON module repository.
@Feng2015 used a combination of occurrence data from GBIF, and additional occurrence data manually collected from the published literature.
Unfortunately the latter data have not been made publically available, so here we use only data from GBIF.
If the additional data had been made available it would be straightforward to incorporate them, for example using the `LocalOccurrenceData` module.

@@

  # get dataframe & index to presence data
  df <- na.omit(.data$df)
  pres_idx <- which(df$type == 'presence')

@@

  # get index to rows in sub_df, update the full dataset and return
  pres_keep_idx <- rownames(th[[1]])
  .data$df <- rbind(df[pres_idx,][pres_keep_idx, ],
                    df[-pres_idx, ])
  return (.data)
}
```

@@

```{r buildmodule, eval = TRUE, results = 'hide', fig.keep = 'none'} 
BuildModule(object = spThin,
            type = 'process',
            title = 'Spatial thinning of Presence-only Data',
            description = paste('Apply the stochastic spatial thinning',
                                'algorithm implemented in the spThin',
                                'package to presence data in a',
                                'presence-background dataset'),
            details = paste('Full details of the algorithm are available in',
                            'the open-access article by Aiello-Lammens',
                            'et al. (2015): dx.doi.org/10.1111/ecog.01132'),
            author = 'ZOON Developers',
            email = 'zoonproject@gmail.com',
            paras = list(thin = paste('Thinning parameter - the required',
                         'minimum distance (in kilometres) between points',
                         'after applying the thinning procedure')),
            dataType = 'presence-only',
            check = TRUE)
```

This module can now be shared so that others can use it in their ZOON workflows. The best way of sharing it is via the `zoon` modules repository. Modules can uploaded there, via the module submission system at [URL TBD].
